---
title: "Self-disclosure mediates AM and depression - Data Analysis"
author: "Uyen Doan"
date: "29/11/2022"
output: html_document
editor_options: 
  chunk_output_type: inline
---
#Set-up

```{r}
#here::i_am()
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(haven)
library(psych)
library(dplyr)
library(foreign)
library(ggplot2)
library(Hmisc)
library(nortest)
library(naniar)
library(mice)
library(miceadds)
library(VIM)
library(lavaan)
library(lattice)
library(mitml)
library(readr)
d_full <- read_sav("Hitchcock_16June2022.sav")
d_add <- read_sav("B3980_Hitchcock_23June2023.sav")
source("process.R")

options(scipen = 999)
```

```{r create data frame, include=FALSE}
d1 <- d_add %>% select (c(cidB3980, kz021, c800, f8ws112, c645, r9020, matdep_recurrent, pq1010, pq1011, a_happ_5g, b_bore_5g, c_reli_5g, d_hope_5g, e_exci_5g, f_fail_5g, g_lone_5g, h_sad_5g, i_luck_5g, j_rela_5g, ccr500, ccr501, ccr502, ccr510, ccr511, ccr512, ccr520, ccr521, ccr522, ccr523, ccr530, ccr531, ccr532, ccr533, ccr534, ccr535, ccr540, ccr550, ccs4500, ccs4502, ccs4503, ccs4504, ccs4505, ccs4506, ccs4508, ccs4509, ccs4511, ccs4512, ccs4513, ccs4514, ccs4515, ff6500, ff6502, ff6503, ff6504, ff6505, ff6506, ff6508, ff6509, ff6511, ff6512, ff6513, ff6514, ff6515, ccs6530, ccs6590, ccs6600, ccs6610, ccs6620, tb7030, tb7031, tb7032, tb7033, tb7034, tb7035, tb7036, tb7037, tb7038, tb7039, tb7040, tb7041, tb7042))

d1<- rename(d1, Sex = kz021)
d1<- rename(d1, Ethnicity = c800)
d1<- rename(d1, IQ = f8ws112)
d1<- rename(d1, WeeklyIncome = r9020)
d1<- rename(d1, MumEd = c645)
d1<- rename(d1, MatDep = matdep_recurrent)
d1<- rename(d1, PartnerDep = pq1011)

d <- d1 %>% mutate_at(c('cidB3980', #ID
                        'IQ',
                        #mem spec
                        'a_happ_5g', 'b_bore_5g','c_reli_5g', 'd_hope_5g', 'e_exci_5g', 'f_fail_5g', 'g_lone_5g', 'h_sad_5g', 'i_luck_5g', 'j_rela_5g', 
                        #self-disclosure 14yo
                        'ccr500', 'ccr501', 'ccr502', 'ccr510', 'ccr511', 'ccr512', 'ccr520', 'ccr521', 'ccr522', 'ccr523', 'ccr530', 'ccr531', 'ccr532', 'ccr533', 'ccr534', 'ccr535', 'ccr540', 'ccr550', 
                        #sMFQ 16yo self-report
                        'ccs4500', 'ccs4502', 'ccs4503', 'ccs4504', 'ccs4505', 'ccs4506', 'ccs4508', 'ccs4509', 'ccs4511', 'ccs4512', 'ccs4513', 'ccs4514', 'ccs4515', 
                        #sMFQ 13yo self-report
                        'ff6500', 'ff6502', 'ff6503', 'ff6504', 'ff6505', 'ff6506', 'ff6508', 'ff6509', 'ff6511', 'ff6512', 'ff6513', 'ff6514', 'ff6515', 
                        'ccs6530', #self-harm
                        'ccs6620', 'ccs6590', 'ccs6600', 'ccs6610', #suicide planning
                        #K-SADS 14yo parent-report
                        'tb7030', 'tb7031', 'tb7032', 'tb7033', 'tb7034', 'tb7035', 'tb7036', 'tb7037', 'tb7038', 'tb7039', 'tb7040', 'tb7041', 'tb7042',
                        #demographic
                        'Sex', 'Ethnicity', 'WeeklyIncome', 'MatDep', 'PartnerDep', 'MumEd'), as.numeric) 

class(d$b_bore_5g)

```

# Data cleaning and wrangling

```{r, include=FALSE}
length(d$a_happ_5g)
sum(is.na(d$a_happ_5g))

# remove participants with missing memory data
d_short <- d %>% filter(!(a_happ_5g == -9999))

#code NA as NA
d_short <- d_short %>% 
  mutate(WeeklyIncome = na_if(WeeklyIncome, 11),
         MatDep = na_if(MatDep, -9999),
         famDep = case_when(MatDep == 1 ~ 1,
                            PartnerDep == 1 | PartnerDep == 2 ~ 1,
                            is.na(MatDep) & is.na(PartnerDep) ~ NA,
                            .default = 0),
         ccr540 = na_if(ccr540, 9),
         ccr550 = na_if(ccr550, 9),
         tb7031 = na_if(tb7031, 9),
         tb7032 = na_if(tb7032, 9),
         tb7033 = na_if(tb7033, 9),
         tb7034 = na_if(tb7034, 9),
         tb7035 = na_if(tb7035, 9),
         tb7036 = na_if(tb7036, 9),
         tb7037 = na_if(tb7037, 9),
         tb7038 = na_if(tb7038, 9),
         tb7039 = na_if(tb7039, 9),
         tb7040 = na_if(tb7040, 9),
         tb7041 = na_if(tb7041, 9),
         tb7042 = na_if(tb7042, 9))
```

Internal consistency for support seeking questionnaire (order: female caregiver, male caregiver, parents, and total)

```{r internal consistency, echo=FALSE}
#Female, male and parent/caregiver sharing of experiences
d_FCS <- data.frame(d$ccr500, d$ccr501, d$ccr502)
d_MCS <- data.frame(d$ccr510, d$ccr511, d$ccr512)
d_PS <- data.frame(d$ccr520, d$ccr521, d$ccr522, d$ccr523)
d_totalsharing <-
  data.frame(
    d$ccr500,
    d$ccr501,
    d$ccr502,
    d$ccr510,
    d$ccr511,
    d$ccr512,
    d$ccr520,
    d$ccr521,
    d$ccr522,
    d$ccr523
  )

#cronbach's alpha for the scale (using the psych package)
psych::alpha(d_FCS)$total$std.alpha
psych::alpha(d_MCS)$total$std.alpha
psych::alpha(d_PS)$total$std.alpha
psych::alpha(d_totalsharing)$total$std.alpha
```

## Re-coding
```{r reversed coding, include=FALSE}
#support seeking scale: higher score = more support seeking
d_short <- d_short %>% mutate(rCcr500 = 5-ccr500,
                              rCcr501 = 5-ccr501,
                              rCcr502 = 5-ccr502,
                              rCcr510 = 5-ccr510,
                              rCcr511 = 5-ccr511,
                              rCcr512 = 5-ccr512,
                              rCcr520 = 6-ccr520,
                              rCcr521 = 6-ccr521,
                              rCcr522 = 6-ccr522,
                              rCcr523 = 6-ccr523)
```

```{r reversed scoring of the MFQ age 13 and 16, include=FALSE}
#mood and feeling questionnaire: higher score = more depression
#age 16
d_short <- d_short %>% mutate(rCcs4500 = 3- ccs4500,
                              rCcs4502 = 3- ccs4502,
                              rCcs4503 = 3- ccs4503,
                              rCcs4504 = 3- ccs4504,
                              rCcs4505 = 3- ccs4505,
                              rCcs4506 = 3- ccs4506,
                              rCcs4508 = 3- ccs4508,
                              rCcs4509 = 3- ccs4509,
                              rCcs4511 = 3- ccs4511,
                              rCcs4512 = 3- ccs4512,
                              rCcs4513 = 3- ccs4513,
                              rCcs4514 = 3- ccs4514,
                              rCcs4515 = 3- ccs4515)
#age 13
d_short <- d_short %>% mutate(rFf6500 = 3-ff6500,
                              rFf6502 = 3-ff6502,
                              rFf6503 = 3-ff6503,
                              rFf6504 = 3-ff6504,
                              rFf6505 = 3-ff6505,
                              rFf6506 = 3-ff6506,
                              rFf6508 = 3-ff6508,
                              rFf6509 = 3-ff6509,
                              rFf6511 = 3-ff6511,
                              rFf6512 = 3-ff6512,
                              rFf6513 = 3-ff6513,
                              rFf6514 = 3-ff6514,
                              rFf6515 = 3-ff6515)

```

```{r reverse coding for depressive symptoms at ~14yo}
d_short <- d_short %>%
  mutate(across(c(tb7030:tb7042), ~ 3 - .x, .names = "r{col}"))
```

```{r reverse code for self-harm and suicide, include=FALSE}
# self-harm: 0 = has not hurt themself, 1 =  has hurt themself
#suicide attempts: 0 = has not made plan before, 1 = has made plan before
d_short <- d_short %>% mutate(
  selfHarm = 2 - ccs6530,
  Suicide = if_else(ccs6590 == 2 |
                      ccs6600 == 2 | ccs6610 == 2 | ccs6620 == 2, 0, 1)
)
```

```{r compute relevant variables, include=FALSE}
#total scores on support seeking and MFQ at 13 and 16
#higher MFQ = less depression symptoms
#higher totalrSS = more support seeking
#higher totalSS = less support seeking
d_short <- d_short %>%
  mutate (
    totalrSS = rowSums(across(c(rCcr500:rCcr523))),
    totalrSS = ifelse(totalrSS == 0, NA, totalrSS),
    totalrMFQt2 = rowSums (across(c(rCcs4500:rCcs4515))),
    totalrMFQt1 = rowSums(across(c(rFf6500:rFf6515))),
    totaldep14 = rowSums (across(c(rtb7030:rtb7042))),
    totaldep14 = ifelse(totaldep14 == 0, NA, totaldep14)
  )
```

```{r calculate memory specificity, include=FALSE}
#number of specific memories recalled (total)
d_short <-
  d_short %>% mutate(totalMem = rowSums(across (
    c(
      a_happ_5g,
      b_bore_5g,
      c_reli_5g,
      d_hope_5g,
      e_exci_5g,
      f_fail_5g,
      g_lone_5g,
      h_sad_5g,
      i_luck_5g,
      j_rela_5g
    )
  ) == '4'))

#number and proportion (out of 5) of specific positive and negative memories
d_short <-
  d_short %>% mutate(negMem = rowSums (across(
    c(b_bore_5g, d_hope_5g, f_fail_5g, g_lone_5g, h_sad_5g)
  ) == "4"),
  posMem = rowSums(across(
    c(a_happ_5g, c_reli_5g, e_exci_5g, i_luck_5g, j_rela_5g)
  ) == "4"))
```

# Data Analysis - Pre-registered method (PROCESS)
## Mediation model 1
```{r Hyp 1}
# reversed Support seeking mediation model Hypothesis 1
process(
  data = d_short,
  y = "totalrMFQt2",
  x = "totalMem",
  m = "totalrSS",
  cov = "totalrMFQt1",
  total = 1,
  stand = 1,
  normal = 1,
  model = 4,
  seed = 10000,
  progress = 0
)
```

### Exploratory follow-up models

```{r Hyp 1 follow-up}
#negative memory -> reversed support seeking -> depression (reversed MFQ)
process(
  data = d_short,
  y = "totalrMFQt2",
  x = "negMem",
  m = "totalrSS",
  cov = "totalrMFQt1",
  total = 1,
  stand = 1,
  normal = 1,
  model = 4,
  seed = 10000,
  progress = 0
)
```

```{r Hyp 1 follow-up2}
#positive memory -> reversed support seeking -> depression (reversed MFQ)
process(
  data = d_short,
  y = "totalrMFQt2",
  x = "posMem",
  m = "totalrSS",
  cov = "totalrMFQt1",
  total = 1,
  stand = 1,
  normal = 1,
  model = 4,
  seed = 10000,
  progress = 0
)
```

## Moderated Mediation model 3

```{r, warning=F}
#graph interactions of mediation models with sex
ggplot(d_short) +
  aes(x=totalMem, y=totalrSS, color = as.factor(Sex))+
  geom_jitter(color = "grey")+
  geom_smooth(method = "lm", data = filter(d_short, Sex == 1))+
  geom_smooth(method = "lm", data = filter(d_short, Sex == 2))

ggplot(d_short) +
  aes(x=totalrSS, y=totalrMFQt2, color = as.factor(Sex))+
  geom_jitter(color = "grey")+
  geom_smooth(method = "lm", data = filter(d_short, Sex == 1))+
  geom_smooth(method = "lm", data = filter(d_short, Sex == 2))
```

```{r Hyp 2}
#regression models for Hyp 2
mod1 <- d_short$Sex* d_short$totalMem
mod2 <- d_short$Sex* d_short$totalrSS
d_short <- data.frame(d_short, mod1, mod2)

summary(lm(totalrMFQt2 ~ totalMem+totalrSS+Sex+mod1+mod2+totalrMFQt1, data = d_short))
```

```{r Hyp 2 2}
#conditional process model
# 1 = male, 2 = female
process(
  data = d_short,
  y = "totalrMFQt2",
  x = "totalMem",
  m = "totalrSS",
  w = "Sex",
  cov = c("totalrMFQt1"),
  total = 1,
  normal = 1,
  model = 58,
  seed = 10000,
  progress = 0
)

```

## Mediation models 3
```{r Hyp 3 - self-harm}
process(
  data = d_short,
  y = "selfHarm",
  x = "totalMem",
  m = "totalrSS",
  cov = c("totalrMFQt1", "totalrMFQt2"),
  total = 1,
  normal = 1,
  model = 4,
  seed = 10000,
  progress = 0
)
```

```{r calculating odds ratio}
#self-harm ~ support seeking
exp(-0.0441)
exp(-0.0441+1.96*0.0087)
exp(-0.0441-1.96*0.0087)

exp(0.0342)
exp(0.0342 + 1.96*0.0218)
exp(0.0342 - 1.96*0.0218)

#suicide planning ~ support seeking
#b path
exp(-0.0417)
exp(-0.0417+1.96*0.0161)
exp(-0.0417-1.96*0.0161)
# direct effect
exp(0.0735)
exp(0.0735+1.96*0.0439)
exp(0.0735-1.96*0.0439)

```

```{r Hyp 3 - suicide}
process(
  data = d_short,
  y = "Suicide",
  x = "totalMem",
  m = "totalrSS",
  cov = c("totalrMFQt1", "totalrMFQt2"),
  total = 1,
  normal = 1,
  model = 4,
  seed = 10000,
  progress = 0
)

```

# Using MICE and lavaan 
```{r}
#make a dataset with relevant variables only
data <- d_short[, c(2:6, 82, 132:136, 138:140)]

data <-
  data %>% mutate_at(
    c(
      "Sex",
      "Ethnicity",
      "MumEd",
      "WeeklyIncome",
      "famDep",
      "selfHarm",
      "Suicide"
    ),
    as.factor
  )

aggr_plot <-
  aggr(
    data,
    col = c('skyblue', 'lightpink'),
    numbers = TRUE,
    sortVars = TRUE,
    labels = names(data),
    cex.axis = .7,
    gap = 3,
    ylab = c("Histogram of missing data", "Pattern")
  )

naniar::prop_miss(data [,-c(13, 14)])
```
## MICE
```{r}
# imp_method = c(
#   "logreg",
#   "polyreg",
#   "pmm",
#   "polyreg",
#   "polyreg",
#   "logreg",
#   "logreg",
#   "logreg",
#   "pmm",
#   "pmm",
#   "pmm",
#   "pmm",
#   "pmm",
#   "pmm"
# )
# 
# d_imp <- mice(data,
#               m = 20,
#               method = imp_method,
#               seed = 3108)
# print(d_imp)
# write.mice.imputation(d_imp, name = "d_imp_save", mids2spss = F)
```

```{r}
load("d_imp_save/d_imp_save.Rdata")
d_imp = mi.res
```

```{r}
#checking imp datasets
bwplot(d_imp)
densityplot(d_imp)
xyplot(d_imp, selfHarm ~ totalrSS | as.factor(.imp))
xyplot(d_imp, Suicide ~ totalrSS | as.factor(.imp))
```

```{r create imputed dataframe}
imp.df <- datlist_create(d_imp)
corr_mice <- micombine.cor(d_imp, variables = c(3,9:14))
```

##Fitting mediation model 1
```{r, warning=F}
#specify mediation model
med1 <- '
totalrMFQt2 ~ c*totalMem + Sex + IQ + totalrMFQt1 + famDep + WeeklyIncome
totalrSS ~ a*totalMem + Sex + IQ + totalrMFQt1 + famDep + WeeklyIncome
totalrMFQt2 ~ b*totalrSS
ab :=  a*b
total := c + (a*b)
'

#apply simultaneously to all imp datasets
imp.med.model1 <- lapply(
  imp.df,
  FUN = function(data) {
    res <-
      sem(med1,
          ordered = c("WeeklyIncome", "famDep", "Sex"),
          data = data)
    return(res)
  }
)

#extract relevant parameters for imp datasets
results.imp.med.model1 <- testEstimates(imp.med.model1)
print(results.imp.med.model1, digits = 4)
confint.mitml.testEstimates(results.imp.med.model1)

#apply same model for completed dataset
com.med.model1 <- sem(model = med1, data = d_short)
summary(com.med.model1)
```

### Follow-up models with memory valence
```{r, warning=F}
#specify mediation model with positive mem
med1a <- '
totalrMFQt2 ~ c*posMem + Sex + IQ + totalrMFQt1 + famDep + WeeklyIncome
totalrSS ~ a*posMem + Sex + IQ + totalrMFQt1 + famDep + WeeklyIncome
totalrMFQt2 ~ b*totalrSS
ab :=  a*b
total := c + (a*b)
'

#apply simultaneously to all datasets
imp.med.model1a <- lapply(
  imp.df,
  FUN = function(data) {
    res <-
      sem(med1a,
          ordered = c("WeeklyIncome", "famDep", "Sex"),
          data = data)
    return(res)
  }
)

#extract relevant parameters
results.imp.med.model1a <- testEstimates(imp.med.model1a)
print(results.imp.med.model1a, digits = 4)

#apply same model for completed dataset
com.med.model1a <-
  sem(
    model = med1a,
    ordered = c("WeeklyIncome", "famDep", "Sex"),
    data = d_short
  )
summary(com.med.model1a)

```

```{r, warning=F}
#specify mediation model with negative mem
med1b <- '
totalrMFQt2 ~ c*negMem + Sex + IQ + totalrMFQt1 + famDep + WeeklyIncome
totalrSS ~ a*negMem + Sex + IQ + totalrMFQt1 + famDep + WeeklyIncome
totalrMFQt2 ~ b*totalrSS
ab :=  a*b
total := c + (a*b)
'

#apply simultaneously to all datasets
imp.med.model1b <- lapply(
  imp.df,
  FUN = function(data) {
    res <-
      sem(med1b,
          ordered = c("WeeklyIncome", "famDep", "Sex"),
          data = data)
    return(res)
  }
)

#extract relevant parameters
results.imp.med.model1b <- testEstimates(imp.med.model1b)
print(results.imp.med.model1b, digits = 4)

#apply same model for completed dataset
com.med.model1b <-
  sem(
    model = med1b,
    ordered = c("WeeklyIncome", "famDep", "Sex"),
    data = d_short
  )
summary(com.med.model1b)

```

## Moderated mediation model
```{r}
#make interaction terms for model 2
##imputed dataset
sexSS <- function(data) {
  data$sexSS = as.numeric(data$Sex) * data$totalrSS
  return(data)
}

sexMem <- function(data) {
  data$sexMem = as.numeric(data$Sex) * data$totalMem
  return(data)
}

imp.df <- lapply(imp.df, sexSS)
imp.df <- lapply(imp.df, sexMem)
##complete case dataset
d_short <- d_short %>% mutate(sexSS = as.numeric(Sex) * totalrSS,
                              sexMem = as.numeric(Sex) * totalMem)
```

```{r, warning=F}
mod.med2 <- '
totalrMFQt2 ~ b1*totalrSS + b2*Sex + b3*sexSS + cprime*totalMem + IQ + totalrMFQt1 + famDep + WeeklyIncome
totalrSS ~ a1*totalMem + a2*Sex + a3*sexMem + IQ + totalrMFQt1 + famDep + WeeklyIncome


# index of moderated mediation
IndModMed1:= a1*b3+a3*b1
IndModMed2:= a3*b3


# simple slope of totalrSS on totalMem is a1+a3*Sex
aMale: = a1+a3*1
aFemale: = a1+a3*2


# simple slope of totalrMFQt2 on totalSS is b1+b3*Sex
bMale: = b1+b3*1
bFemale: = b1+b3*2


# conditional indirect effects is a*(b1+b3*Sex)
abMale: = aMale*bMale
abFemale: = aFemale*bFemale
'

imp.mod.med.model2 = lapply(
  imp.df,
  FUN = function(data) {
    res = sem(mod.med2,
              data = data,
              ordered = c("WeeklyIncome", "famDep"))
    return(res)
  }
)

#extract relevant parameters
results.imp.mod.med.model2 <- testEstimates(imp.mod.med.model2)
print(results.imp.mod.med.model2, digits = 4)

#apply same model for completed dataset
com.mod.med.model2 <-
  sem(
    model = mod.med2,
    ordered = c("WeeklyIncome", "famDep"),
    data = d_short
  )
summary(com.mod.med.model2)
```

## Mediation models with behavioural outcomes
```{r self-harm, warning=F}
# mediation model with self-harm
med3a <- '
selfHarm ~ c*totalMem + Sex + IQ + totalrMFQt1 + totalrMFQt2 + famDep + WeeklyIncome
totalrSS ~ a*totalMem + Sex + IQ + totalrMFQt1 + famDep + WeeklyIncome
selfHarm ~ b*totalrSS
ab :=  a*b
total := c + (a*b)
'

#apply simultaneously to all datasets
med.imp.model3a <- lapply(
  imp.df,
  FUN = function(data) {
    res <-
      sem(
        med3a,
        ordered = c("WeeklyIncome", "famDep", "selfHarm", "Sex"),
        data = data
      )
    return(res)
  }
)

#extract relevant parameters
results.imp.med.model3a <- testEstimates(med.imp.model3a)
print(results.imp.med.model3a, digits = 4)
confint.mitml.testEstimates(results.imp.med.model3a)
exp(-0.141) #OR b path
exp(-0.141 + 1.96 * 0.051)
exp(-0.141 - 1.96 * 0.051)
exp(0.018)  #OR c'
exp(0.018 + 1.96 * 0.013)
exp(0.018 - 1.96 * 0.013)


#apply same model for completed dataset
com.med.model3a <-
  sem(
    model = med3a,
    ordered = c("WeeklyIncome", "famDep", "selfHarm", "Sex"),
    data = d_short
  )
summary(com.med.model3a)
```

```{r suicide, warning=F}
# mediation model with suicide planning
med3b <- '
Suicide ~ c*totalMem + Sex + IQ + totalrMFQt1 + totalrMFQt2 + famDep + WeeklyIncome
totalrSS ~ a*totalMem + Sex + IQ + totalrMFQt1 + famDep + WeeklyIncome
Suicide ~ b*totalrSS
ab :=  a*b
total := c + (a*b)
'

#apply simultaneously to all datasets
med.imp.model3b <- lapply(
  imp.df,
  FUN = function(data) {
    res <-
      sem(
        med3b,
        ordered = c("WeeklyIncome", "famDep", "Suicide", "Sex"),
        data = data
      )
    return(res)
  }
)

#extract relevant parameters
results.imp.med.model3b <- testEstimates(med.imp.model3b)
print(results.imp.med.model3b, digits = 4)
exp(-0.035) #OR b path
exp(-0.035 + 1.96 * 0.045)
exp(-0.035 - 1.96 * 0.045)
exp(0.039)  #OR c' path
exp(0.039 + 1.96 * 0.018)
exp(0.039 - 1.96 * 0.018)


#apply same model for completed dataset
com.med.model3b <-
  sem(
    model = med3b,
    ordered = c("WeeklyIncome", "famDep", "Suicide", "Sex"),
    data = d_short
  )
summary(com.med.model3b)
```
##exploratory model with memory valence for suicide planning

```{r, warning = F}
#positive mem
med4a <- '
Suicide ~ c*posMem + Sex + IQ + totalrMFQt1 + totalrMFQt2 + famDep + WeeklyIncome
totalrSS ~ a*posMem + Sex + IQ + totalrMFQt1 + famDep + WeeklyIncome
Suicide ~ b*totalrSS
ab :=  a*b
total := c + (a*b)
'

#apply simultaneously to all datasets
med.imp.model4a <- lapply(
  imp.df,
  FUN = function(data) {
    res <-
      sem(
        med4a,
        ordered = c("WeeklyIncome", "famDep", "Suicide", "Sex"),
        data = data
      )
    return(res)
  }
)

#extract relevant parameters
results.imp.med.model4a <- testEstimates(med.imp.model4a)
print(results.imp.med.model4a)

#apply same model for completed dataset
com.med.model4a <-
  sem(
    model = med4a,
    ordered = c("WeeklyIncome", "famDep", "Suicide", "Sex"),
    data = d_short
  )
summary(com.med.model4a)
```

```{r, warning=F}
#negative mem
med4b <- '
Suicide ~ c*negMem + Sex + IQ + totalrMFQt1 + totalrMFQt2 + famDep + WeeklyIncome
totalrSS ~ a*negMem + Sex + IQ + totalrMFQt1 + famDep + WeeklyIncome
Suicide ~ b*totalrSS
ab :=  a*b
total := c + (a*b)
'

#apply simultaneously to all datasets
med.imp.model4b <- lapply(
  imp.df,
  FUN = function(data) {
    res <-
      sem(
        med4b,
        ordered = c("WeeklyIncome", "famDep", "Suicide", "Sex"),
        data = data
      )
    return(res)
  }
)

#extract relevant parameters
results.imp.med.model4b <- testEstimates(med.imp.model4b)
print(results.imp.med.model4b)

#apply same model for completed dataset
com.med.model4b <-
  sem(
    model = med4b,
    ordered = c("WeeklyIncome", "famDep", "Suicide", "Sex"),
    data = d_short
  )
summary(com.med.model4b)
```

```{r, warning=FALSE}
#regression models
##negative memory
reg1 <- '
Suicide ~ negMem + Sex + IQ + totalrMFQt1 + totalrMFQt2 + famDep + WeeklyIncome
'

#apply simultaneously to all datasets
reg.imp.model1 <- lapply(
  imp.df,
  FUN = function(data) {
    res <-
      sem(
        reg1,
        ordered = c("WeeklyIncome", "famDep", "Suicide", "Sex"),
        data = data
      )
    return(res)
  }
)

#extract relevant parameters
results.imp.reg.model1 <- testEstimates(reg.imp.model1)
print(results.imp.reg.model1, digits = 4)
exp(0.079)
exp(0.079 + 1.96 * 0.030)
exp(0.079 - 1.96 * 0.030)

#apply same model for completed dataset
com.reg.model1 <-
  sem(
    model = reg1,
    ordered = c("WeeklyIncome", "famDep", "Suicide", "Sex"),
    data = d_short
  )
summary(com.reg.model1)
```

```{r, warning=FALSE}
#regression models
##positive memory
reg2 <- '
Suicide ~ posMem + Sex + IQ + totalrMFQt1 + totalrMFQt2 + famDep + WeeklyIncome
'

#apply simultaneously to all datasets
reg.imp.model2 <- lapply(
  imp.df,
  FUN = function(data) {
    res <-
      sem(
        reg2,
        ordered = c("WeeklyIncome", "famDep", "Suicide", "Sex"),
        data = data
      )
    return(res)
  }
)

#extract relevant parameters
results.imp.reg.model2 <- testEstimates(reg.imp.model2)
print(results.imp.reg.model2, digits = 4)
exp(0.031)
exp(0.031 + 1.96 * 0.031)
exp(0.031 - 1.96 * 0.031)

#apply same model for completed dataset
com.reg.model2 <-
  sem(
    model = reg2,
    ordered = c("WeeklyIncome", "famDep", "Suicide", "Sex"),
    data = d_short
  )
summary(com.reg.model2)
```

```{r}
d_short %>% ggplot(mapping = aes(x = as.factor(Suicide), y = totalMem)) +
  geom_jitter()

d_short %>% ggplot(mapping = aes(x = as.factor(Suicide), y = negMem)) +
  geom_jitter() +
  geom_violin()

d_short %>% ggplot(mapping = aes(x = as.factor(Suicide), y = posMem)) +
  geom_jitter()

```

##exploratory model with memory valence for self-harm
```{r, warning=F}
#positive mem
med5a <- '
selfHarm ~ c*posMem + Sex + IQ + totalrMFQt1 + totalrMFQt2 + famDep + WeeklyIncome
totalrSS ~ a*posMem + Sex + IQ + totalrMFQt1 + famDep + WeeklyIncome
selfHarm ~ b*totalrSS
ab :=  a*b
total := c + (a*b)
'

#apply simultaneously to all datasets
med.imp.model5a <- lapply(
  imp.df,
  FUN = function(data) {
    res <-
      sem(
        med5a,
        ordered = c("WeeklyIncome", "famDep", "selfHarm", "Sex"),
        data = data
      )
    return(res)
  }
)

#extract relevant parameters
results.imp.med.model5a <- testEstimates(med.imp.model5a)
print(results.imp.med.model5a, digits = 4)

#apply same model for completed dataset
com.med.model5a <-
  sem(
    model = med5a,
    ordered = c("WeeklyIncome", "famDep", "selfHarm", "Sex"),
    data = d_short
  )
summary(com.med.model5a)
```

```{r, warning = F}
#negative mem
med5b <- '
selfHarm ~ c*negMem + Sex + IQ + totalrMFQt1 + totalrMFQt2 + famDep + WeeklyIncome
totalrSS ~ a*negMem + Sex + IQ + totalrMFQt1 + famDep + WeeklyIncome
selfHarm ~ b*totalrSS
ab :=  a*b
total := c + (a*b)
'

#apply simultaneously to all datasets
med.imp.model5b <- lapply(
  imp.df,
  FUN = function(data) {
    res <-
      sem(
        med5b,
        ordered = c("WeeklyIncome", "famDep", "selfHarm", "Sex"),
        data = data
      )
    return(res)
  }
)

#extract relevant parameters
results.imp.med.model5b <- testEstimates(med.imp.model5b)
print(results.imp.med.model5b, digits = 4)

#apply same model for completed dataset
com.med.model5b <-
  sem(
    model = med5b,
    ordered = c("WeeklyIncome", "famDep", "selfHarm", "Sex"),
    data = d_short
  )
summary(com.med.model5b)
```

# Descriptive statistics
```{r}
data = d_short[, c(1:6, 82, 132:140)]
data = data %>%
  mutate(across(
    c(
      "famDep",
      "Sex",
      "Ethnicity",
      "MumEd",
      "WeeklyIncome",
      "selfHarm",
      "Suicide"
    ),
    as.factor
  ))

summary_stats <- sapply(data, function(x) {
  if (is.numeric(x)) {
    stats <- c(
      mean = mean(x, na.rm = TRUE),
      sd = sd(x, na.rm = TRUE),
      n = sum(!is.na(x))
    )
  } else {
    freq <- table(x)
    percent <- freq / 5785 * 100
    stats <- cbind(freq, percent)
  }
  return(stats)
})

d_scIncome <-
  data %>% count(WeeklyIncome, name = 'N') %>% mutate (perc = N / 5785 * 100)

d_scIncomeSum <-
  d_scIncome %>% mutate(economicDisadvantage = if_else(as.numeric(WeeklyIncome) < 4, "yes", "no")) %>%
  group_by(economicDisadvantage) %>% summarise(n = sum(N), prop = sum(perc)) %>% ungroup
```

## Exploring data patterns

Checking MFQ at 13 for participants who continued vs those who did not

```{r missing data, echo=FALSE}
#compute missing data in MFQt2
data <- data %>% mutate(naMFQ = if_else(is.na(totalrMFQt2), 0, 1))
#t.test(formula = totalMem ~ naMFQ, data = d_short)
missing_MFQ <-
  t.test(formula = totalrMFQt1 ~ naMFQ,
         data = data,
         exact = TRUE)
print(missing_MFQ)
missing_MFQ$p.value
missing_MFQ$estimate / sqrt(missing_MFQ$parameter + 1) # cohen's d
```

```{r descriptive stats}
#correlation matrix between study variables
data.cor = data[, c(
  "Sex",
  "Ethnicity",
  "MumEd",
  "famDep",
  "WeeklyIncome",
  "IQ",
  "totalMem",
  "posMem",
  "negMem",
  "totalrMFQt1",
  "totalrSS",
  "totalrMFQt2",
  "selfHarm",
  "Suicide"
)]
cormatrix  <- rcorr(as.matrix(data.cor))
cormatrix$r
cormatrix$P

n.var = sapply(data.cor, function(x)
  sum(!is.na(x)))
n.var
```

```{r checking linearity}
summary(lm(totalrMFQt2 ~ totalrSS, d_short))
summary(lm(totalrMFQt2 ~ totalrSS + totalMem, d_short))

d_short %>% ggplot(mapping = aes(x = totalMem, y = totalrSS)) +
  geom_jitter(size = 0.5, na.rm = TRUE) + theme_classic()

d_short %>% ggplot(mapping = aes(x = totalrSS, y = totalrMFQt2)) +
  geom_jitter(size = 0.5, na.rm = TRUE) + theme_classic()

d_short %>% ggplot(mapping = aes(x = as.factor(selfHarm), y = totalrMFQt2)) +
  geom_violin() + theme_classic()
```
